INTELLIGENT SYSTEMS

### 2021-04-08 paper_5.tex
finish  5.4.4

\subsubsection{Identity Authentication}
An authentication process begins by submitting a sample of input to CNN. 
Within this, there may be a layer that will produce a vector of features. 
To find out which layer it is, a cross-validation process is performed. Once 
extracted, the features are normalized with the L2 standard. Subsequently 
a vector is calculated containing the Euclidean distances between the values 
given in input and those present in the training set. In order to calculate the 
\emph{Area Under Curve} (AUC) or the \emph{Equal-Error-Rate} (EER), these distances 
are transformed into probabilities.

@@

    \item \emph{Multi-task with Fusion} (+ Task, + Sensor): the last experiment consists in applying the fusion in a multitasking context within the network. In this case it will be necessary to train a CNN for all three existing tasks. From the results shown in table \ref{table accuracy and F1 (+ Task, + Sensor)}, this architecture manages to achieve better performance than the others mentioned above, this is because the model has much more information (labels and inputs) to describe people. The strength of this architecture is that it manages to return a result for each task.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2} & \bfseries{93.8} & \bfseries{96.3} & \bfseries{97.7} & \bfseries{95.9}\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (1 Task, + Sensor).}
        \label{table accuracy and F1 (+ Task, + Sensor)}
    \end{table}

\end{enumerate}

>>>>

\subsubsection{Identity Authentication}\label{IA}
An authentication process begins by submitting a sample of input to CNN. 
Within this, there may be a layer that will produce a vector of features. 
To find out which layer it is, a cross-validation process is performed. Once 
extracted, the features are normalized with the L2 standard. Subsequently 
a vector is calculated containing the Euclidean distances between the values 
given in input and those present in the training set. In order to calculate the 
\emph{Area Under Curve} (AUC) or the \emph{Equal-Error-Rate} (EER), these distances 
are transformed into probabilities.

@@

    \item \emph{Multi-task with Fusion} (+ Task, + Sensor): the last experiment consists in applying the fusion in a multitasking context within the network. In this case it will be necessary to train a CNN for all three existing tasks. From the results shown in table \ref{table accuracy and F1 (+ Task, + Sensor)}, this architecture manages to achieve better performance than the others mentioned above, this is because the model has much more information (labels and inputs) to describe people. The strength of this architecture is that it manages to return a result for each task.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2} & \bfseries{93.8} & \bfseries{96.3} & \bfseries{97.7} & \bfseries{95.9}\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (1 Task, + Sensor).}
        \label{table accuracy and F1 (+ Task, + Sensor)}
    \end{table}
\end{enumerate}

\subsubsection{Authentication Experiments}
In paragraph \ref{IA} we said that to see if two different samples belong to the 
same subject, an identity authentication process must be carried out. In 
other words, it is necessary to evaluate the goodness of a model by calculating 
the AUC and EER index. To do this, one had to first calculate the 
Euclidean distances between the sample vector present in the test set with 
the sample vectors present in the training set. Subsequently, it was necessary 
to transform these distances into probabilities that will be represented 
on a ROC curve. Once this is done, for each model previously described, 
the values for AUC (the higher the better) and EER (the lower the better), 
calculated on the ROC curve, are shown in table \ref{Authentication}. 
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c|cc|}
        \hline
        Architecture & EER & AUC\\
        \hline
        SingleTask Accelerometer & 1.47 & 99.91\\
        SingleTask Gyroscope & 2.50 & 99.80\\
        \hline
        MultiTask Accelerometer & 1.61 & 99.90\\
        MultiTask Gyroscope & 2.85 & 99.72\\
        \hline
        SingleTask Fusion & \bfseries{1.14} & \bfseries{99.93}\\
        \hline
        MultiTask Fusion & 1.34 & 99.92\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Authentication accuracy.}
    \label{Authentication}
\end{table}
